%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Medium Length Graduate Curriculum Vitae
% LaTeX Template
% Version 1.1 (9/12/12)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Rensselaer Polytechnic Institute (http://www.rpi.edu/dept/arc/training/latex/resumes/)
%
% Important note:
% This template requires the res.cls file to be in the same directory as the
% .tex file. The res.cls file provides the resume style used for structuring the
% document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[margin, 10pt]{res} % Use the res.cls style, the font size can be changed to 11pt or 12pt here

\usepackage{helvet} % Default font is the helvetica postscript font
%\usepackage{newcent} % To change the default font to the new century schoolbook postscript font uncomment this line and comment the one above

\setlength{\textwidth}{5.1in} % Text width of the document

\begin{document}

%----------------------------------------------------------------------------------------
%	NAME AND ADDRESS SECTION
%----------------------------------------------------------------------------------------

\moveleft.5\hoffset\centerline{\large\bf Oguzhan Ulusoy} % Your name at the top
  
\moveleft.5\hoffset\centerline{Istanbul, Turkey} % Your address

\moveleft\hoffset\vbox{\hrule width\resumewidth height 1pt}\smallskip % Horizontal line after name; adjust line thickness by changing the '1pt'

%----------------------------------------------------------------------------------------

\begin{resume}

%----------------------------------------------------------------------------------------
%	CONTACT INFORMATION SECTION
%----------------------------------------------------------------------------------------
 
\section{Contact Information}  

E-mail: ulusoyoguzhan@gmail.com \\
Skype: oguz-ulusoy

%----------------------------------------------------------------------------------------
%	WEB PAGES SECTION
%----------------------------------------------------------------------------------------
 
\section{Web Pages}  

Personal Site:  http://www.oguzhanulusoy.com \\
Medium: http://medium.com/@oguzhanulusoy \\
Linkedin:  http://linkedin.com/in/oguzhanulusoy \\
Github:  http://github.com/oguzhanulusoy 

%----------------------------------------------------------------------------------------
%	INTEREST SECTION
%----------------------------------------------------------------------------------------
 
\section{Interests}  

Machine Learning, Software Architecture Design, Backend Development, Database Modelling, Futurism, Productivity

%----------------------------------------------------------------------------------------
%	SKILLS SECTION
%----------------------------------------------------------------------------------------
 
\section{Skills}  

\textbf{Experience: }Java, Java EE, JSF, Python, Django, C\#,  \\ElasticSearch, Logstash, Kibana, Beats, Docker, Linux, OSX, \\Git, ClearCase, Jira, Confluence, Bitbucket, Jenkins, \\JavaScript, JQuery, Bootstrap, CSS, HTML5 \\Oracle Database, Microsoft SQL Server, 

\textbf{Familiarity: }PHP, ASP, Perl, Flask, .Net, MySQL, SQLite3
 
%----------------------------------------------------------------------------------------
%	PROFESSIONAL EXPERIENCE SECTION
%----------------------------------------------------------------------------------------
 
\section{Experience}
Netaş \hfill \textit{January 2020 - present} \\
{\sl Java Software Engineer} \\
Worked on Application Server project which includes Voice over Internet (VoIP), Unified Communications (UC), web based real-time communication (WebRTC) and moving telecommunications to the cloud.

\begin{itemize} \itemsep -2pt % Reduce space between items
\item Involved in documentation and feature implementation with test driven\\ development using SIP rules.
\item Contributed to code base and implemented sustaining and bug fixing with agile development strategies.
\item Involved in defect management by reviewing pull requests.
\end{itemize}
 
Worked on Central Logging project that is a part of SAYEM project which provides many smart city use-cases. 
\begin{itemize} 
\item Gathered business requirements, prepared Requirements Document.
\item Involved in implementation, integration and documentation.
\item Stack: Docker, Apache Kafka, ElasticSearch, Logstash, Kibana, Beats, Python, pandas
\end{itemize} 

R\&D Center, Işık Üniversitesi \hfill \textit{September 2018 - January 2020} \\
{\sl Software Engineer} \\
Worked on E-Campus project at Center for Education Technologies. E-Campus is a new generation student system integrated with government services.
\begin{itemize}
\item Designed system architecture and algorithms.
\item Prepared three database schemas and implemented stored procedures, maintenance planning, triggers, jobs and alerts.
\item Developed backend and frontend with microservice architecture.
\item Applied domain driven development with agile methodologies.
\item  Led 6 fresh engineer and 4 interns.
\end{itemize} 

%----------------------------------------------------------------------------------------
%	STARTUP EX SECTION
%----------------------------------------------------------------------------------------

\section{Startup Ex}

Assessment Center \hfill \textit{January 2019 - June 2019} \\
Given Amazon Web Services and ISACA certification exams (prepared by PSI) for candidates in Turkey and Middle East. 

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\section{Education}

{\sl } Işık University, Istanbul, Turkey \\
2018 - 2021 (Expected) :  M.Sc., Computer Engineering (\%100 scholarship) 
\begin{itemize}
\item GPA: 3.00 / 4.00 
\item Thesis Topic:  Modelling ER Diagram by NLP 
\item Supervisor:  Assoc. Prof. Emine Ekin 
\end{itemize}

{\sl } Işık University, Istanbul, Turkey \\
2015 - 2018 :  B.Sc., Computer Engineering (\%100 scholarship) 
\begin{itemize}
\item GPA: 2.7 / 4.00  
\item Thesis Topic:  Student Information System for Institutes  
\item Supervisor:  Assoc. Prof. M.Taner Eskil 
\item Assistant student in Computer Science department in Işık Üniversitesi between September 2016 and March 2017. Supported freshman and sophomore level students in Fundamentals of Programming and Object Oriented Programming courses. 
\item Achieved EUR-ACE® certificate.
\end{itemize}

{\sl } Işık University, Istanbul, Turkey \\
2014 - 2015 :  Prep School  
\begin{itemize}
\item GPA: 86 / 100 
\item Achieved Pearson Assured  certificate.
\end{itemize}

%----------------------------------------------------------------------------------------
%	HACKATHON SECTION
%----------------------------------------------------------------------------------------

\section{Hackathon}

Netaş, Netrd \hfill \textit{2020} \\
Involved in artificial intelligence hackathon and developed a GAN project.

 %----------------------------------------------------------------------------------------
%	HOBBIES AND INTERESTS SECTION
%----------------------------------------------------------------------------------------

\section{Hobbies and Interests}

Productivity  Techniques, Electronics, Computer Science, Futurism, Video Games, Healthy  Living,  Personal  Growth

%----------------------------------------------------------------------------------------

\end{resume}
\end{document}